---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# respirometr

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/773406370.svg)](https://zenodo.org/doi/10.5281/zenodo.13235277)
[![R-CMD-check](https://github.com/roaldarbol/respirometr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/roaldarbol/respirometr/actions/workflows/R-CMD-check.yaml)
[![respirometr status
badge](https://roaldarbol.r-universe.dev/badges/respirometr)](https://roaldarbol.r-universe.dev)
[![Codecov test coverage](https://codecov.io/gh/roaldarbol/respirometr/graph/badge.svg)](https://app.codecov.io/gh/roaldarbol/respirometr)
<!-- badges: end -->

*An R toolbox for analysing respirometry data*

The primary aim of the *respirometr* package is to provide a standardised workflow for analysing respirometry data in a *tidyverse*-friendly syntax. 

## Installation

You can install the development version of *respirometr* with:

Type | Source | Command
---|---|-----------------------
Development | R-universe | `install.packages('respirometr', repos = c('https://roaldarbol.r-universe.dev', 'https://cloud.r-project.org'))`
Development | Github | `renv::install("roaldarbol/respirometr")`

Once you have installed the package, you can load it with:

```{r, eval=FALSE}
library("respirometr")
```

## Documentation

See our docs to go through the workflow, one-by-one:

- [Introduction to `respirometr`](https://www.roald-arboel.com/respirometr/articles/respirometr.html)
- [Read respirometry data](https://www.roald-arboel.com/respirometr/articles/read-licor.html)
- [Combine with movement data]()

## Status
> **Warning**
>
> 🏗️ The package is currently in early development and the interface is subject to change. Feel free to play around and provide feedback.


## Contribute

**If your favourite type of respirometry data or model of respirometer is not currently supported, we'd love to get a sample of your data to support it!** 

If you enjoy the package, please make sure to [cite it](#citation). If you find a bug, feel free to open an issue.

<!-- ## Acknowledgements -->

<!-- *animovement* is all about the data, and we are deeply grateful for all those who have shared data with us to implement and test our code. Thank you! -->

<!-- - [Stan Edwards](): Trackball with optical flow, free. -->
<!-- - [Estelle Moubarak](): Trackball with optical flow, fixed. -->
<!-- - [Maria Cozan](): Treadmill with rotary encoder. -->
<!-- - [Violette Chiara](): AnimalTA -->

## Citation {#citation}

To cite *respirometr* in publications use:

```{r}
citation("respirometr")
```
